An agent-based model for city networks based on interactions between firms

### 2019-09-26 slides.tex
.

World city network driven by interactions between firms (Taylor, 2001; Martinus and Sigler, 2018)

@@

% discussion theorie Denise

@@

\begin{equation}
     p_{ij} \propto \left(\frac{E_{i}}{E}\right)^{\gamma_F} \cdot \left(\frac{E_{j}}{E}\right)^{\gamma_T} \cdot \left(\frac{w_{ij}}{W}\right)^{\gamma_W} \cdot s(S_{ik},S_{jk})^{\gamma_S} \cdot \exp \left(- \gamma_D \cdot d_{ij}\right) \cdot \exp \left(- \gamma_G \cdot g_{ij}\right)
\end{equation}

@@

@@

@@

@@

Good convergence for most indicators: average sharpes ratios on a one-factor sampling above 5 (except for metropolization index $\simeq 1.5$)

@@

@@

@@

\textbf{Open repository} at

@@

>>>>

World city network driven by interactions between firms \cite{taylor2001specification} \cite{martinus2018global}

@@

@@

\begin{equation}
     p_{ij} \propto \left(\frac{E_{i}}{E}\right)^{\gamma_F} \cdot \left(\frac{E_{j}}{E}\right)^{\gamma_T} \cdot \left(\frac{w_{ij}}{W}\right)^{\gamma_W} \cdot s\left(S_{ik},S_{jk}\right)^{\gamma_S} \cdot \exp \left(- \gamma_D \cdot d_{ij}\right) \cdot \exp \left(- \gamma_G \cdot g_{ij}\right)
\end{equation}

@@

\textit{Following \cite{raimbault2018space}, geosimulation models must be studied within synthetic controllable urban contexts (spatial sensitivity)}

@@

\begin{itemize}
	\item Model implemented in NetLogo (good compromise interactivity / ergonomy), with fast data structures (matrix/table extensions)
	\item Integrated into OpenMOLE \cite{reuillon2013openmole} for model exploration
	\item Current implementation: only network dynamics 
\end{itemize}

@@

	\medskip

	\textit{Networks at $t=1500$, for default parameters values and high gravity (left) and low gravity (right)}

@@

$\rightarrow$ Good convergence for most indicators: average sharpes ratios on a one-factor sampling above 5 (except for metropolization index $\simeq 1.5$)

@@

\textbf{Practical application}

\textbf{Developments}

@@

$\rightarrow$ A simulation model to understand processes of network emergence

@@

\textbf{Open repository for model and results at}

@@

\textbf{Simulation data at}

\texttt{}% dataverse
